A new tidy data structure to support exploration and modeling of temporal data

### 2019-01-12 main.Rmd
added pipeline flowcharts to flights section

A closer examination of some big airports across the US will give an indication about how well the busiest airports manage the outflow traffic on a daily basis. A subset that contains observations for Houston (IAH), New York (JFK), Kalaoa (Hawaii), Los Angeles (LAX) and Seatle (SEA) airports is obtained first. The succeeding operations compute delayed percentages every day at each airport, which are framed as grey lines in Figure \@ref(fig:sel-monthly-plot). Winter months tend to fluctuate a lot compared to the summer across all the airports. What superimposes on these lines is two-month moving averages so that a temporal trend is more visible. The number of days for each month is variable. Moving averages for two months call for computing weighted mean. But this can also be accomplished using a pair of commonly used verbs--`nest()` and `unnest()` to handle list-columns, without worrying weights specification. The sliding operation with large window size smoothes out the fluctuations and gives a stable trend around 25% over the year. The LAX airport has seen a gradual decline in delays over the year, whereas the SEA airport has a steady control of delays over time. The IAH and JFK airports have undergone more delays in the middle of year, while the KOA has the inverse pattern with higher delay percentage in both ends of the year.

@@

@@

>>>>

A closer examination of some big airports across the US will give an indication about how well the busiest airports manage the outflow traffic on a daily basis. A subset that contains observations for Houston (IAH), New York (JFK), Kalaoa (KOA), Los Angeles (LAX) and Seatle (SEA) airports is obtained first. The succeeding operations compute delayed percentages every day at each airport, which are framed as grey lines in Figure \@ref(fig:sel-monthly-plot). Winter months tend to fluctuate a lot compared to the summer across all the airports. What superimposes on these lines is two-month moving averages so that a temporal trend is more visible. The number of days for each month is variable. Moving averages for two months call for computing weighted mean. But this can also be accomplished using a pair of commonly used verbs--`nest()` and `unnest()` to handle list-columns, without worrying weights specification. The sliding operation with large window size smoothes out the fluctuations and gives a stable trend around 25% over the year. The LAX airport has seen a gradual decline in delays over the year, whereas the SEA airport has a steady control of delays over time. The IAH and JFK airports have undergone more delays in the middle of year, while the KOA has the inverse pattern with higher delay percentage in both ends of the year.

@@

```{r flight-pipeline2, fig.cap = "(ref:flight-pipeline2-cap)"}
include_graphics("img/flight-pipeline2")
```

(ref:flight-pipeline2-cap) Flow chart illustrates the pipeline that pre-processes the data for creating Figure \ref{fig:sel-monthly-plot}.

@@

```{r flight-pipeline3, fig.cap = "(ref:flight-pipeline3-cap)"}
include_graphics("img/flight-pipeline3")
```

(ref:flight-pipeline3-cap) Flow chart illustrates the pipeline that pre-processes the data for creating Figure \ref{fig:draw-qtl}.
